### 2015-07-10 narrative/intro.tex
intro minor changes

Central to our approach is giving users the ability to define the importance, or utility of their data    
 \S\ref{sec:data-description}.
This includes the ability to assign varying levels of importance to individual data objects in their entirety, or to specific
subsets and pieces.
Key research challenges include: 1) developing an expressive and easy to use programinterface, 2) formulating a system model that can support 
autonomic decision, for example, for saving data based on user-defined importance and utility of data~\S~\ref{sec:managing-data-life})
, and 3) the interface between the system and the back-end storage across both single, and multiple running applications~\S~\ref{sec:qos}.

 %
  In our  scenario we would like the scientist would then specify a set of rules that governed the actual behavior while the simulation is running.
If the system resources are available and the estimated write times are in order, the write can proceed.
Or, the write can be postponed to a later time-step, or data reduced via in situ techniques can be saved.
Data importance or utility will be used to place the various data on the proper SSIO layer.
The user specified lifetime for each data ensures that the data with the highest utility is preserved in fast storage
for the longest period of time, and the least utility are migrated to lower layers in the storage hierarchy.
%
%Since the data will be a collection of objects placed on the storage system,
%some of the objects will be broken up into multiple pieces by ``plug-ins''
%to the system which will allow data to be characterized first in terms of the most
%important pieces, and then by subsequent levels of detail. We can think of this as
%something similar to an Adaptive Mesh Refinement scheme which keeps track of
%the places where there are features such as steep gradients, which contain large errors on the
%coarser views, as opposed to other areas with smaller errors. These distinctions allow us to make decisions
%about which sub-objects to save (all of the data, which will then go to
%different layers) or just some of the sub-objects? The research questions
%are numerous: How does the user specify their intentions? How does the user
%prioritize the different sub-objects of the data? Where does the data go
%into the storage hierarchy? Does the data get replicated in the lower tiers
%of the hierarchy? When the user specifies the time they want the data saved,
%how does this get into the storage system?

\paragraph{Storage System Perspective}
\label{subsec:storage-perspective}
From the perspective of the storage system, it is necessary to manage the data from
a given user request amongst all of the requests from all users, and try to optimize the
entire system accordingly. Today the problem is that when a user writes there is a
tremendous amount of interference from other users on the system who may be
writing or reading at the same time, leading to unpredictable performance.
By requiring a certain QoS, the system could potentially lock out and throttle other users. 
The storage system must also automatically move data from one tier of the storage to
another, without affecting the QoS that was offered at request
time. The storage system must be able to organize
data amongst all of the tiers of storage in a known, consistent way.

One of our research objectives is to understand how the
storage system can interact with the middleware   so
that the data with the highest utility is kept on the fastest layers of the
storage system for as long as specified. We need to maintain 
QoS and therefore, be able to provide fuzzy estimates of the time it will take to write/read data from
the different layers to inform any migration/eviction decisions, and it
is also critical that the storage system can manage (discover and retrieve) the data across all of the
layers automatically, without user intervention. 
Central to our approach is that the storage system needs to define bounds of time estimates
(min time, max time), and as our system evolves, we want to allow plug-ins which can help
reduce the range of the bounds, and furthermore, with optimizations we would like to minimize 
the times for both reading and writing. Thus, we want predictable performance, and methods
which can obtain better performance bounds in time.

@@

\paragraph{Reading  Perspective}
\label{subsec:reading-perspective}
From the perspective of reading, this project will look at both
simulation restart and post-processing. For the former case,
we will allow both traditional file-based approach leveraging fast storage tier
such as NVRAM (non-volatile RAM), and memory-based approach via retrieving
data directly from NVRAM. For the latter case,
an important aspect is that they want a reduction of latency and they
require a certain amount of QoS as well. When someone is
doing interactive analysis and expects that the data they read in is about
10s, but it turns into 1,000s, the user typically tends to either wait
another day for doing their analysis or gets frustrated and reads much less
data than they really need to. Furthermore the user tends to read in just a
small sample of the data without much knowledge if they are missing
important pieces of the data.

>>>>

Central to our approach is giving users the ability to define the utility of their data    
 \S\ref{sec:data-description}.
This includes the ability to assign varying levels of importance to individual data objects in their entirety, or to specific
subsets and pieces.
Key research challenges include: 1) developing an expressive and easy to use program interface, 2) formulating a system model that can support 
autonomic decision, for example, for saving data based on user-defined importance and utility of data~\S~\ref{sec:managing-data-life}),
 and 3) the interface between the system and the back-end storage across both single, and multiple running applications~\S~\ref{sec:qos}.

 %
  In our  scenario we would like the scientist would then specify a set of rules that governed the actual behavior while the simulation is running.
If the system resources are available and the estimated write times are in order, the write can proceed.
%Or, the write can be postponed to a later time-step, or data reduced via in situ techniques can be saved.
Data  utility will be used to place the various data on the proper SSIO layer.
The user specified lifetime for each data ensures that the data with the highest utility is preserved in fast storage
for the longest period of time, and the least utility are migrated to lower storage  layers.
%
%Since the data will be a collection of objects placed on the storage system,
%some of the objects will be broken up into multiple pieces by ``plug-ins''
%to the system which will allow data to be characterized first in terms of the most
%important pieces, and then by subsequent levels of detail. We can think of this as
%something similar to an Adaptive Mesh Refinement scheme which keeps track of
%the places where there are features such as steep gradients, which contain large errors on the
%coarser views, as opposed to other areas with smaller errors. These distinctions allow us to make decisions
%about which sub-objects to save (all of the data, which will then go to
%different layers) or just some of the sub-objects? The research questions
%are numerous: How does the user specify their intentions? How does the user
%prioritize the different sub-objects of the data? Where does the data go
%into the storage hierarchy? Does the data get replicated in the lower tiers
%of the hierarchy? When the user specifies the time they want the data saved,
%how does this get into the storage system?

\paragraph{Storage System Perspective}
\label{subsec:storage-perspective}
From the perspective of the storage system, it is necessary to manage the data from
a given user request amongst all of the requests from all users, and try to optimize the
entire system accordingly. Today the problem is that when a user writes there is a
tremendous amount of interference from other users on the system who may be
writing or reading at the same time, leading to unpredictable performance.
By requiring a certain QoS~\S\ref{sec:qos}, the system could potentially lock out and throttle other users. 
The storage system must also automatically move data from one tier of the storage to
another, without affecting the QoS that was offered at request
time. The storage system must be able to organize
data amongst all of the tiers of storage in a known, consistent way.

One of our research objectives is to understand how the
storage system can interact with the middleware   so
that the data with the highest utility is kept on the fastest layers of the
storage system for as long as specified. We need to maintain 
QoS and therefore, be able to provide fuzzy estimates of the time it will take to write/read data from
the different layers to inform any migration/eviction decisions, and it
is also critical that the storage system can manage (discover and retrieve) the data across all of the
layers automatically, without user intervention. 
Central to our approach is that the storage system needs to define bounds of time estimates
(min time, max time), and as our system evolves, we want to allow plug-ins which can help
reduce the range of the bounds, and furthermore, with optimizations we would like to minimize 
the times for both reading and writing. Thus, we want predictable performance, and methods
which can obtain better performance bounds in time. Furthermore, since our system will place chunks
in all of the tiers  we need to quickly discover where the data is in the hierarchy~\S\ref{sec:naming-discovery}

@@

\paragraph{Reading  Perspective}
\label{subsec:reading-perspective}
From the perspective of reading, this project will look at both
CR  and post-processing I/O patterns. For the former case,
we will allow both traditional file-based approach leveraging fast storage tier
such as NVRAM (non-volatile RAM), and memory-based approach via retrieving
data directly from NVRAM. For the latter case,
an important aspect is that they want a reduction of latency and they
require a certain amount of QoS as well. When someone is
doing interactive analysis and expects that the data they read in is about
10s, but it turns into 1,000s, the user typically tends to either wait
another day for doing their analysis or gets frustrated and reads much less
data than they really need to. Furthermore the user tends to read in just a
small sample of the data without much knowledge if they are missing
important pieces of the data~\S\ref{sec:migration}.
